Improving Software Maintainability through Automated Refactoring of Code Clones

### 2020-01-10 ecoop/paper.tex
Updates from Overleaf

@@

\author{}
\authorrunning{Siimon :)}

@@

%\author{Simon Baars}
%\affiliation{\institution{University of Amsterdam}}
%\email{simon.mailadres@gmail.com}

%\author{Ana Oprescu}
%\affiliation{\institution{University of Amsterdam}}
%\email{a.m.oprescu@uva.nl}

@@

\subsection{Clone refactoring}
Krishnan et al.~\cite{krishnan2013refactoring} approach clone refactoring as an optimization problem: how variability between cloned fragments influences the refactoring techniques required and their implications on system design. The main focus of this study is to find out which clones \textbf{can} be refactored. We extend this work by looking into which clones \textbf{should} be refactored. We propose definitions for refactorable clones together with thresholds to be able to limit their negative impact on system design. We measure which clones improve maintainability when refactored. This results in a set of thresholds that can be used to detect and refactor clones that should be refactored.
%The state-of-the-art in code clone refactoring is the work by Mazinanian et al.~\cite{mazinanian2016jdeodorant}. The authors propose a tool named JDeodorant that can automatically refactor a subset of duplication problems. This tool is based on several studies that look into different aspects of code clone refactoring. In a study by Krishnan et al.~\cite{krishnan2013refactoring} clone refactoring is approached as an optimization problem: how variability between cloned fragments influences the refactoring techniques required and their implications on system design. Another study by Krishnan et al.~\cite{krishnan2014unification} proposes a list of preconditions for clones to determine their refactorability. This list is revised by Tsantalis et al.~\cite{tsantalis2015assessing}, proposing a set of 8 preconditions that determine whether two duplicated fragments can be refactored.

@@

\begin{figure}[H]
  \includegraphics[width=1\columnwidth]{img/flow}
  \caption{Abstract flow diagram of CR.}
  \label{fig:clonerefactorflow}
\end{figure}

@@

@@

\begin{table}[H]
\centering
\begin{tabular}{@{}llrr@{}}
\toprule
\textit{\textbf{Category}} & \textit{\textbf{Location}} & \textit{\textbf{Clone instances}} & \textit{\textbf{Total}} \\ \midrule
\multirow{2}{*}{Partial} & Partial Method & 219,540 & \multirow{2}{*}{229,521} \\ \cmidrule(lr){2-3}
 & Partial Constructor & 9,981 &  \\ \midrule
\multirow{5}{*}{Full} & Full Method & 12,990 & \multirow{5}{*}{13,173} \\ \cmidrule(lr){2-3}
 & Full Interface & 64 &  \\ \cmidrule(lr){2-3}
 & Full Constructor & 58 &  \\ \cmidrule(lr){2-3}
 & Full Class & 37 &  \\ \cmidrule(lr){2-3}
 & Full Enum & 24 &  \\ \midrule
\multirow{3}{*}{Other} & Several Methods & 22,749 & \multirow{3}{*}{53,773} \\ \cmidrule(lr){2-3}
 & Only Fields & 17,700 &  \\ \cmidrule(lr){2-3}
 & Other & 13,324 &  \\ \bottomrule
\end{tabular}
\caption{Number of clone instances for clone location categories}
\label{tab:location}
\end{table}

@@

>>>>

\usepackage{etoolbox}
\AtBeginEnvironment{quote}{\singlespacing\footnotesize\ttfamily}

\bibliographystyle{plainurl}

@@

%\author{Anonymous Author}
%\authorrunning{Anonymous Author}
\author{Anonymous Author(s)}{-}{-}{-}{-}

\authorrunning{Anonymous Author(s)}

\Copyright{Anonymous Author(s)}

@@

@@

\subsection{Clone refactoring}
Krishnan et al.~\cite{krishnan2013refactoring} approach clone refactoring as an optimization problem: how variability between cloned fragments influences the refactoring techniques required and their implications on system design. The main focus of this study is to find out which clones \textbf{can} be refactored. We extend this work by looking into which clones \textbf{should} be refactored. We propose definitions for refactorable clones together with thresholds to be able to limit their negative impact on system design. We measure which clones improve maintainability when refactored. This results in a set of thresholds that can be used to detect and refactor clones that should be refactored.

For refactoring clones, we took naming the extracted method outside of the scope of the study. To have this not influence the results, the metrics that determine the maintainability of an applied refactoring do not measure the quality of the name of the extracted method. 
%The state-of-the-art in code clone refactoring is the work by Mazinanian et al.~\cite{mazinanian2016jdeodorant}. The authors propose a tool named JDeodorant that can automatically refactor a subset of duplication problems. This tool is based on several studies that look into different aspects of code clone refactoring. In a study by Krishnan et al.~\cite{krishnan2013refactoring} clone refactoring is approached as an optimization problem: how variability between cloned fragments influences the refactoring techniques required and their implications on system design. Another study by Krishnan et al.~\cite{krishnan2014unification} proposes a list of preconditions for clones to determine their refactorability. This list is revised by Tsantalis et al.~\cite{tsantalis2015assessing}, proposing a set of 8 preconditions that determine whether two duplicated fragments can be refactored.

@@

\begin{figure}[H]
  \includegraphics[width=0.7\columnwidth]{img/flow}
  \caption{Abstract flow diagram of CR.}
  \label{fig:clonerefactorflow}
\end{figure}

@@

\subsection{Refactoring evaluation}
To evaluate the refactorings applied by CR and their impact, we expanded CR to create a git-commit for each applied transformation. We then use the ``Github Desktop''\footnote{GitHub Desktop is a git client: \url{https://desktop.github.com/}} to visualize each change made by CR (see Fig.~\ref{fig:cr_refactoring}). We then checked samples of the applied refactorings and the calculated metrics.

\begin{figure}[H]
    \centering
    \includegraphics[width=1\columnwidth]{img/cr.png}
    \caption{Automatically applied refactoring by CR shown in the GitHub Desktop client. CR automatically authors a git commit for each applied transformation and specifies the impact of the change in the commit message.}
    \label{fig:cr_refactoring}
\end{figure}

The full commit message for the refactoring example displayed in Fig.~\ref{fig:cr_refactoring} is as follows:
\begin{quote}
CloneRefactor refactored a clone class with 2 clone instances. For the common code we created a new method and named this method “cloneRefactor0". These clone instances have a Same Method relation with each other. The newly created method has been placed in ISODateTimeFormat. Each duplicated fragment has been replaced with a call to this method.
\\ \\
== System Quality Metrics == \\
Total Cyclomatic Complexity increased by 1 from 6,994 to 6,995.\\
Total Unit Interface Size increased by 1 from 3,715 to 3,716.\\
Total Unit Line Size increased by 1 from 23,024 to 23,025.\\
Total Unit Token Size decreased by 2 from 153,190 to 153,188.\\
Total Nodes decreased by 1 from 18,866 to 18,865.\\
\\
Duplicated Nodes decreased by 6 from 502 to 496.\\
Duplicated Tokens decreased by 42 from 5,064 to 5,022.\\
Duplicated Lines decreased by 6 from 504 to 498.\\
\\
== Risk Profiles ==\\
Unit Complexity\\
Created a new method with a low risk Unit Complexity of 1.\\
Removing duplicate blocks changed 1 method.\\
The method "dateByWeek(DateTimeFormatterBuilder, Collection, boolean, boolean)" went from 8 to 8 Unit Complexity. This did not influence the risk category of this method, it is still low risk.\\
\\
Line Volume\\
Created a new method with a low risk Line Volume of 5.\\
Removing duplicate blocks changed 1 method.\\
The method "dateByWeek(DateTimeFormatterBuilder, Collection, boolean, boolean)" went from 47 to 39 Line Volume. This did not influence the risk category of this method, it is still high risk.\\
\\
Token Volume\\
Created a new method with a low risk Token Volume of 30.\\
Removing duplicate blocks changed 1 method.\\
The method "dateByWeek(DateTimeFormatterBuilder, Collection, boolean, boolean)" went from 303 to 271 Token Volume. This increased the risk category of this method from high to moderate.\\
\\
The new method has a low risk Unit Interface Size of 1.\\
\\
Duplication went from 2.66\% to 2.63\%. This did not influence the risk category of the duplication in this codebase, it is still low risk.
\end{quote}

@@

\begin{table}
\centering
\begin{tabular}{@{}llrr@{}}
\toprule
\textit{\textbf{Category}} & \textit{\textbf{Location}} & \textit{\textbf{Clone instances}} & \textit{\textbf{Total}} \\ \midrule
\multirow{2}{*}{Partial} & Partial Method & 219,540 & \multirow{2}{*}{229,521} \\ \cmidrule(lr){2-3}
 & Partial Constructor & 9,981 &  \\ \midrule
\multirow{5}{*}{Full} & Full Method & 12,990 & \multirow{5}{*}{13,173} \\ \cmidrule(lr){2-3}
 & Full Interface & 64 &  \\ \cmidrule(lr){2-3}
 & Full Constructor & 58 &  \\ \cmidrule(lr){2-3}
 & Full Class & 37 &  \\ \cmidrule(lr){2-3}
 & Full Enum & 24 &  \\ \midrule
\multirow{3}{*}{Other} & Several Methods & 22,749 & \multirow{3}{*}{53,773} \\ \cmidrule(lr){2-3}
 & Only Fields & 17,700 &  \\ \cmidrule(lr){2-3}
 & Other & 13,324 &  \\ \bottomrule
\end{tabular}
\caption{Number of clone instances for clone location categories}
\label{tab:location}
\end{table}

@@

\subsection{Future Work}
